\documentclass[10pt,sans,letterpaper]{moderncv}

\usepackage[margin=0.3in]{geometry}

\moderncvstyle{classic}
\moderncvcolor{orange}
\moderncvicons{awesome}

\setlength{\hintscolumnwidth}{1in}

\def\cpp{C\texttt{++}}

\name{Denton}{Liu}
\email{denton.liu@edu.uwaterloo.ca}
\homepage{dentonliu.com}
\social[linkedin]{DentonL}
\social[github]{Denton-L}

\begin{document}
\makecvtitle
\vspace{-3\baselineskip}

\section{Technical Skills}
\cvlistitem{Proficient in C, \cpp{}, Python, Go, Bash, Java and various assembly languages (x86, 6502, ARM, PIC, AVR).}
\cvlistitem{Experienced with using Git, Docker, CMake, GDB and Valgrind.}
\cvlistitem{Knowledgeable in FPGA development using Verilog including bringing up a RISC-V core.}
\cvlistitem{Well-versed in cryptocurrency blockchain technology with an emphasis on Ethereum development.}
\cvlistitem{Longtime Arch Linux user with abundant experience using the command line.}

\vspace{-0.5\baselineskip}
\section{Experience}
\cventry{Jan -- Apr 2019}{Blockchain and Networking Software Engineering Intern}{Marconi Protocol}{San Francisco, California}{}{}
\cvlistitem{Identified and patched a security vulnerability that resulted in overpayment in servers running open-ethereum-pool.}
\cvlistitem{Patched fork of go-ethereum to implement custom work-fetching protocol, fixing the above security issue.}
\cvlistitem{Decreased build time of Docker image from 20 to 4 seconds by parallelising and caching each component build.}
\cvlistitem{Debugged and fixed deep race condition that caused clients to disconnect because of duplicate work being sent.}
\cvlistitem{Integrated C libraries with React Native in Android by creating a Java bridge using the Java Native Interface.}

\cventry{Apr -- Aug 2018}{Embedded Systems Engineering Intern}{Bose Corporation}{Framingham, Massachusetts}{}{}
\cvlistitem{Programmed I\textsuperscript{2}C support in new products allowing slave chips to be reflashed from master processor.}
\cvlistitem{Integrated Python debugging tool into the \cpp{} manufacturers' test library.}
\cvlistitem{Improved codebase quality by integrating linters and warning checks into the continuous integration system.}

\cventry{Jan -- Apr 2018}{Undergraduate Research Assistant}{University of Waterloo}{Waterloo, Ontario}{}{}
\cvlistitem{Implemented Karatsuba multiplication and Barrett reduction cryptography primitives using 8-bit AVR assembly.}
\cvlistitem{Removed timing attacks from the implemented cryptographic primitives while also decreasing number of instructions.}

\cventry{Sept -- Dec 2017}{Embedded Security Developer}{ESCRYPT - Embedded Security}{Waterloo, Ontario}{}{}
\cvlistitem{Reverse-engineered messages on car's CAN bus to create demo that could lock and unlock doors.}
\cvlistitem{Improved code quality by aggressively enabling warnings in build system and fixing the result.}

\cventry{Jan -- Apr 2017}{Engineering Intern}{Cask Data}{Palo Alto, California}{}{}
\cvlistitem{Designed and implemented optimiser to remove unnecessary operations by building and analysing graphs.}
\cvlistitem{Reduced memory usage of searches by 50\% which stopped YARN containers from running out of memory.}
\cvlistitem{Assisted with system administration and project releases by creating useful and maintainable shell scripts.}

\cventry{May -- Aug 2016}{Blockchain Engineering}{Ledger Labs}{Toronto, Ontario}{}{}
\cvlistitem{Committed many successful pull requests to the Solidity compiler in \cpp{}.}
\cvlistitem{Contributed to open-source Ethereum projects in JS including browser-solidity, solc-js and testrpc.}

\vspace{-0.5\baselineskip}
\section{Projects}
\cvitem{Git Contributions}{
	\begin{itemize}
		\item Contributed to Git by fixing reported bugs, reviewing patches and writing new features in C and shell script.
		\item Improved the \texttt{git rebase} command by implementing \texttt{-{}-keep-base} and adding more fast-forward cases.
		\item Caught and fixed a bug across multiple commands that caused commit messages to be rendered incorrectly.
	\end{itemize}
}
\vspace{-\baselineskip}
\cvitem{Based Connect}{
	\begin{itemize}
		\item Reverse-engineered Bluetooth protocol between official Bose Connect app and headphones using Wireshark.
		\item Analysed compiled binaries to discover addresses of servers used to serve firmware updates.
		\item Implemented command line application in Linux using C to control headphones over Bluetooth using BlueZ.
	\end{itemize}
}
\vspace{-\baselineskip}
\cvitem{Cryptocurrency Algorithm Trading}{
	\begin{itemize}
		\item Developed a reliable algorithm-trading application using Python 3 with 8.8\% average monthly return.
		\item Implemented a market making algorithm, taking advantage of the volatile cryptocurrency market.
		\item Emulated and reimplemented Poloniex exchange API endpoints locally to accurately backtest algorithm.
	\end{itemize}
}

\vspace{-1.5\baselineskip}
\section{Education}
\cventry{2015 -- 2020}{Candidate for Bachelors of Software Engineering}{University of Waterloo}{Waterloo, Ontario}{}{}

\vspace{-0.5\baselineskip}
\section{Interests and Hobbies}
\cvlistitem{Avid unicyclist.}
\cvlistitem{Devoted Vim user.}
\cvlistitem{Enthusiastic user of \LaTeX.}

\end{document}
